hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2025-03-06 inst/manuscript/paper.Rmd
add in new figure 2 and corresponding paragraph

Here, we demonstrate the utility three functions--`summarize_temp()`, `plot_check_temp()`, and `check_continuous()`--using a simulated year-long data set (`year_sim`). This dataset contains temperature readings taken every thirty minutes, and its structure (dimensions and first six rows) is shown below:

@@

```{r plot-check-1, echo = TRUE,  fig.cap="Output of hatchR function `plot_check_temp()`, which is used as a visual data check on the raw `year_sim` data set. Users can set custom thresholds for minimum and maximum temperatures (dashed lines).", fig.height= 4, fig.width=6.5}
plot_check_temp(data = year_sim,
                dates = date,
                temperature = temp,
                temp_min = 0, # temp_min and max lines are 
                temp_max = 25) # user customizable
```

@@

```{r, fig.cap="Output of `plot_phenolgy()` function using predicted hatch time from `woody_island` data set."}
plot_phenology(WI_hatch)
```

>>>>

Here, we demonstrate the utility three functions--`summarize_temp()`, `plot_check_temp()`, and `check_continuous()`--using a simulated year-long dataset (`year_sim`). This dataset contains temperature readings taken every thirty minutes, and its structure (dimensions and first six rows) is shown below:

@@

```{r plot-check-1, echo = TRUE,  fig.cap="Output of hatchR function `plot_check_temp()`, which is used as a visual data check on the raw `year_sim` dataset. Users can set custom thresholds for minimum and maximum temperatures (dashed lines).", fig.height= 4, fig.width=6.5}
plot_check_temp(data = year_sim,
                dates = date,
                temperature = temp,
                temp_min = 0, # temp_min and max lines are 
                temp_max = 25) # user customizable
```

@@

```{r, fig.cap="Output of `plot_phenolgy()` function using predicted hatch time from `woody_island` dataset."}
plot_phenology(WI_hatch)
```
